The Chainsmokers’ Musical Evolution

### 2024-10-12 paper/paper.qmd
fixed italics

On the other hand, acousticness remains low across their discography, indicating a consistent use of electronic production and minimal reliance on acoustic instruments. This reinforces their electronic music identity, as seen in albums like Sick Boy and Memories...Do Not Open, where acousticness scores remain close to 0.

>>>>

On the other hand, acousticness remains low across their discography, indicating a consistent use of electronic production and minimal reliance on acoustic instruments. This reinforces their electronic music identity, as seen in albums like *Sick Boy* and *Memories...Do Not Open*, where acousticness scores remain close to 0.
